A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-04-03 analysis/paper/supplementary_latex.Rmd
move list2env

# knitr options
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = paste0(rprojroot::find_rstudio_root_file(), "/analysis/paper/.scratch/")
)
```

```{r "supplementary", echo=FALSE, results='asis', warning=FALSE}
list2env(read_rds(derived_file("sfigs_stables.rds", "paper")), environment())
source(paste0(dynalysis::get_dynalysis_folder(), "/analysis/paper/sfigs_stables.R"))
```

>>>>

# knitr options
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = paste0(rprojroot::find_rstudio_root_file(), "/analysis/paper/.scratch/")
)

list2env(read_rds(derived_file("sfigs_stables.rds", "paper")), environment())
```

```{r "supplementary", echo=FALSE, results='asis'}
source(paste0(dynalysis::get_dynalysis_folder(), "/analysis/paper/sfigs_stables.R"))
```
